The Design, Semantics, and Implementation of \CEU: a Synchronous Reactive Language

### 2015-10-10 paper.tex
based on Esterel => inspired by Esterel

% Title portion
\title{The Design, Semantics, and Implementation of \CEU: a Synchronous Reactive Language based on Esterel}

@@

\begin{abstract}
\CEU is a reactive language based on Esterel that targets constrained embedded 
platforms and ensures safe concurrency by handling threats at compile time.
%
Based on the synchronous programming model, our design allows for a simple 
reasoning about concurrency that enables compile-time analysis and results in 
deterministic and memory-safe programs.
%
% TODO: some uses?
%
We discuss the design of \CEU and propose a formal semantics for its particular 
control mechanisms, such as parallel compositions, finalization, and internal 
events.
%
We also present two implementation back ends:
one aiming for resource efficiency and interoperability with \C,
and another based on a virtual machine that allows remote reprogramming.
\end{abstract}

@@

\CEU is a synchronous reactive language based on Esterel with support for 
multiple concurrent lines of execution known as \emph{trails}.
By reactive, we mean that programs are stimulated by the environment through 
input events that are broadcast to all awaiting trails.
By synchronous, we mean that all trails at any given moment are either reacting 
to the current event or are awaiting another event;
in other words, trails are never reacting to different events.

@@

We presented the design, semantics, and implementation of \CEU, a synchronous 
reactive language based on Esterel targeting constrained embedded systems.

>>>>

% Title portion
\title{The Design, Semantics, and Implementation of \CEU: a Synchronous Reactive Language}

@@

\begin{abstract}
\CEU is a reactive language inspired by Esterel that targets constrained 
embedded platforms and ensures safe concurrency by handling threats at compile 
time.
%
Based on the synchronous programming model, our design allows for a simple 
reasoning about concurrency that enables compile-time analysis and results in 
deterministic and memory-safe programs.
%
% TODO: some uses?
%
We discuss the design of \CEU and propose a formal semantics for its particular 
control mechanisms, such as parallel compositions, finalization, and internal 
events.
%
We also present two implementation back ends:
one aiming for resource efficiency and interoperability with \C,
and another based on a virtual machine that allows remote reprogramming.
\end{abstract}

@@

\CEU is a synchronous reactive language inspired by Esterel with support for 
multiple concurrent lines of execution known as \emph{trails}.
By reactive, we mean that programs are stimulated by the environment through 
input events that are broadcast to all awaiting trails.
By synchronous, we mean that all trails at any given moment are either reacting 
to the current event or are awaiting another event;
in other words, trails are never reacting to different events.

@@

We presented the design, semantics, and implementation of \CEU, a synchronous 
reactive language inspired by Esterel targeting constrained embedded systems.
